### 2019-11-22 3_implementation.tex
More edits.
Edits.

\subsection{MPI}

@@

\subsection{MPI+X}

We provide two MPI+X implementations of Task Bench to evaluate the
performance of hierarchical programming models. Our MPI+OpenMP
implementation uses forall-style parallel loops to execute tasks, but
otherwise follows the CSP implementation above. The code uses shared
memory for data movement within a rank. Our MPI+CUDA implementation
follows an offload model where data is copied to and from the GPU on
every timestep.

@@

OpenMP~\cite{OpenMPSpec40} and OmpSs~\cite{OmpSs11} are programming
models for loop- and task-based parallelism. (OmpSs is
source-compatible with OpenMP.) The implementations use OpenMP 4.0
tasking.  Because tasks have a fixed number of dependencies,
we use a switch statement to implement dynamic dependencies for Task
Bench. For OpenMP, we tested GNU GOMP and Intel KMP and found KMP to be better
performing.

@@

PaRSEC is a task-based programming system supporting two distinct
programming models: \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}.  PTG is a dataflow model in which programmers
write a concise, algebraic description of the tasks and dataflows in
the program. This compressed representation is expanded into a full
task graph by a source-to-source compiler.

In the DTD model, tasks are enumerated in program order (by executing
the program), and dependencies are identified automatically based on
the arguments to tasks. To improve scalability, the program is
executed in SPMD fashion on all nodes, and the user is responsible for
eliding tasks that are not direct predecessors or successors to those
executed on the current node.

In our Task Bench implementation, we evaluate both PTG and DTD models,
as well as a third option based on DTD that has additional manual
optimizations applied to further reduce dynamic checks for what tasks
should be executed on a node, which further improves
scalability.

>>>>

\subsection{MPI and MPI+X}

@@

We provide two MPI+X implementations to evaluate hierarchical
programming models. Our MPI+OpenMP implementation uses forall-style
parallel loops to execute tasks, but otherwise follows the CSP
implementation above. The code uses shared memory for data movement
within a rank. Our MPI+CUDA implementation follows an offload model
where data is copied to and from the GPU on every timestep.

@@

OpenMP~\cite{OpenMPSpec40} and OmpSs~\cite{OmpSs11} are programming
models for loop- and task-based parallelism. (OmpSs is
source-compatible with OpenMP.) Our implementations use OpenMP 4.0
tasking.  Because tasks have a fixed number of dependencies,
we use a switch statement to implement dynamic dependencies for Task
Bench. For OpenMP, we tested GNU GOMP and Intel KMP and found KMP to be better
performing.

@@

PaRSEC supports two distinct
programming models: \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}.  PTG is a dataflow model in which users
write a concise, algebraic description of the tasks and dataflows in
the program. This compressed representation is expanded into a full
task graph by a source-to-source compiler.

In DTD, tasks are enumerated in program order and dependencies are
identified automatically based on task arguments. To improve
scalability, the program is executed in SPMD fashion on all nodes, and
the user is responsible for eliding tasks that are not direct
predecessors or successors to those executed on the current node.

We implement Task Bench with both PTG and DTD, as well as a third
option based on DTD that has additional manual optimizations applied
to further reduce the cost of dynamic checks for task elision.
